ChIP-seq example

### 2019-12-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

The Haar-Fisz method transforms the Poisson counts, then applies
Gaussian wavelet methods to the transformed data.

@@

Next, we apply SMASH to the read counts to estimate the mean and
variance of the underlying signal. It may take several minutes to
complete this step.

@@

Plot the SMASH estimates
------------------------

@@

This next plot shows the intensity function estimated by SMASH (orange
line). The read count data are depicted as light blue circles, in
which the area of each circle is scaled by the number of data points
that fall within each 1.6-kb "bin". (We show counts summarized within
bins because there are too many data points to plot them
individually.)

@@

```{r plot-smash-estimates, fig.height=3, fig.width=9}
create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
                    nbreaks = 80) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```

Based on this plot, it is clear that the the strongest SMASH intensity
estimates align very closely with the peaks found by MACS. Intriguingly,
the SMASH estimates also suggest the presence of several additional
weaker peaks that were not identified by MACS.

We compare the results against those produced by Haar-Fisz
```{r plot-smash-estimates-2, fig.height=3, fig.width=9}
create.chipseq.plot(bppos/1e6,counts,res.hf,(peaks$start + peaks$end)/2e6,
                    nbreaks = 80) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```

>>>>

The Haar-Fisz method transforms the Poisson counts, then applies
Gaussian wavelet methods to the transformed data. Note that this call
can take several minutes to run on a modern desktop computer.

@@

Next, we apply SMASH to the read counts to estimate the mean and
variance of the underlying signal. It could also take several minutes to
complete this step.

@@

Plot the SMASH and Haar-Fisz estimates
--------------------------------------

@@

This next plot shows the intensity functions estimated by SMASH
(orange line) and the Haar-Fisz method (dark blue line). The read
count data are depicted as light blue circles, in which the area of
each circle is scaled by the number of data points that fall within
each 1.6-kb "bin". (We show counts summarized within bins because
there are too many data points to plot them individually.)

@@

```{r plot-smash-estimates, fig.height=3, fig.width=9}
create.chipseq.plot(bppos/1e6,counts,res$est,res.hf,
                    (peaks$start + peaks$end)/2e6,nbreaks = 80) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```

Based on this plot, it is clear that the strongest Haar-Fisz and SMASH
intensity estimates align very closely with the peaks found by
MACS. Intriguingly, the SMASH estimates also suggest the presence of
several additional weaker peaks that were not identified by MACS.
